\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-14 docs/paper.tex
Typo
add tld

\begin{figure}[t]
  \includegraphics[width=\linewidth]{images/apple}
  \includegraphics[width=\linewidth]{images/fakeapple-punycode}
  \centering
  \caption{Apple official website(top) and its homograph(bottom) on Chrome}
  \label{screenshot}
\end{figure}

The major browsers have their own IDN policies to defend against IDN homograph attack.

Google Chrome, starting with Chrome 51, used to display Punycode if certain tests fail on the input URL.
These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
However, Chrome displayed IDNs that consist purely of cyrillic characters normally, which allow IDN homograph attack of this kind.
Starting from version 59, Chrome checks cryl-latin alikes characters only for non-IDN TLDs and block a label made entirely of Latin-look-alike Cryllic letters for non-IDN TLDs.

Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} used to adopt a long whitelist and only display as Unicode all IDN labels within TLDs on it. Currently, the browser uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
As for domain names made entirely of Cryllic letters, Firefox leave this issue to registries to make sure that their customers cannot rip each other off\footnote{\url{https://wiki.mozilla.org/IDN_Display_Algorithm}}.

Internet Explorer\endnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}. %Edge should probably do the same

@@

The Internet Corporation for Assigned Names and Numbers(ICANN) is responsible for the management of domain name system. In 2009, ICANN started to accept the application for internationalized country code top-level domain(IDN ccTLD) for the benefits of non-English speaking people and the first IDN ccTLD was added to DNS root zone in 2010\ref{tld1}.

@@

>>>>

\begin{figure}[t]
  \includegraphics[width=\linewidth]{images/google}
  \includegraphics[width=\linewidth]{images/fakegoogle-punycode}
  \centering
  \caption{Google(top) and its homograph(bottom) on Chrome}
  \label{screenshot}
\end{figure}

The major browsers have their own IDN policies to defend against IDN homograph attack.
Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.

Internet Explorer\endnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.

Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.

Opera\endnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.

@@

The Internet Corporation for Assigned Names and Numbers(ICANN) is an organization responsible for the management of domain name system. In 2009, ICANN started to accept the application for internationalized country code top-level domain(IDN ccTLD) for the benefits of non-English speaking people and the first IDN ccTLD was added to DNS root zone in 2010\ref{tld1}.

@@

Although the vulnerability of homograph has been introduced as early as 2001, most registrant of TLD don't have the policy to defend homograph attack. Only several TLD have published policy to eliminate the potential risk of specific language. For example, .cn .biz, .hk, and all Chinese TLD will activate both traditional Chinese domain and simplified Chinese domain once one of it is registered. Registering with characters in both traditional Chinese and simplified Chinese is not allowed.

- TODO it was found in wiki, but i didn't find source document.
(In .org domain, once one letter is used in the domain, other homograph letters corresponding to the same domain will be prohibited.)
